Ms. No. PSRM-OA-2019-0126.R1 entitled ``Taking Dyads Seriously''

### 2021-02-04 revisionMemo2/revisionLetter.tex

Thank you for the opportunity to revise and resubmit our manuscript once more. We believe the manuscript has benefited from the Reviewers' helpful and thoughtful comments. We have revised the manuscript, taking seriously each individual point raised by the Reviewers. Our comments and responses are shown in \textcolor{blue}{\emph{BLUE}} below each of the points made by the Reviewers.

@@

\include{rev1}
\include{rev2}

>>>>

Thank you for the opportunity to revise and resubmit our manuscript once more. We believe the manuscript has benefited from the Reviewers' helpful and thoughtful comments. We have revised the manuscript, taking seriously the points raised by you and the Reviewers. Our comments and responses are shown in \textcolor{blue}{\emph{BLUE}} below each of the points from your letter.

@@

\include{editor}
\include{rev1}
\include{rev2}
